ms2

### 2017-05-18 ms2/ms2.Rmd
confidence intervals

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(broom, tidy)
```

@@

```{r do_models}
linear_model = function(df, dependent_var, explanatory_vars) {
  f = paste0(dependent_var, ' ~ ', paste0(explanatory_vars, collapse = ' + ')) %>% formula
  lm(formula=f, weights=place_weight, data=df) %>%
    tidy %>%
    select(term, estimate, p.value)
}

spearman_model = function(df, dependent_var, explanatory_var) {
  cor.test(df[[dependent_var]], df[[explanatory_var]], method='spearman') %>%
    tidy %>%
    mutate(term=explanatory_var, method='spearman') %>%
    select(term, estimate, p.value)
}

@@

```{r spearman_models, cache=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_univariate_models, cache=FALSE}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r multivariate_models, cache=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, autodep=TRUE)
import::from(broom, tidy)
```

@@

```{r do_models}
linear_interval = function(model, level) {
  confint(model, level=level) %>%
    tidy %>%
    setNames(c('term', 'ci_low', 'ci_high'))
}

linear_model = function(df, dependent_var, explanatory_vars) {
  f = paste0(dependent_var, ' ~ ', paste0(explanatory_vars, collapse = ' + ')) %>% formula
  m = lm(formula=f, weights=place_weight, data=df)
  tidy(m) %>%
    select(term, estimate, p.value) %>%
    mutate(n=nrow(df)) %>%
    left_join(linear_interval(m, 0.95), by='term')
}

spearman_interval = function(df, rho_name, n_name, level) {
  mada::CIrho(df[[rho_name]], df[[n_name]], level=level) %>%
    tidy %>%
    setNames(c('rho', 'ci_low', 'ci_high')) %>%
    select(-rho)
}

spearman_model = function(df, dependent_var, explanatory_var) {
  cor.test(df[[dependent_var]], df[[explanatory_var]], method='spearman') %>%
    tidy %>%
    mutate(term=explanatory_var, method='spearman') %>%
    mutate(n=nrow(df)) %>%
    group_by(term, estimate, p.value, n) %>%
    do(spearman_interval(., 'estimate', 'n', 0.95)) %>%
    ungroup()
}

@@

```{r spearman_models, cache=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n) %>%
  kable
```

```{r}
results %>%
  filter(model=='spearman') %>%
  mutate(bug_drug=interaction(bug, drug_group)) %>%
  ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip()
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n) %>%
  kable
```

```{r}
results %>%
  filter(model=='univariate', term=='mean') %>%
  arrange(estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>%
  ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip()
```

@@

```{r hrr_univariate_models}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r multivariate_models}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

```{r}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  arrange(estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>%
  ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip()
```

@@

## MRSA clinda

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MRSA', drug_group=='clindamycin') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  #scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  #ylim(10, 45) +
  xlab('clindamycin claims per beneficiary') + ylab('mean percent nonsusceptible MRSA isolates') +
  theme_minimal()
```
